Temporal Graph Cube

### 2023-01-23 TemporalGraphCube/TemporalGraphCube_revision.tex
exp1-23
exp 1-23

\begin{definition}[Temporal Aggregate Network]
	\label{def:temp_aggregate_network}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$ and an aggregation $A'=(A'_1,A'_2,...,A'_n)$ where $A'_i$ equals $A_i$ or $\ast$, the obtained temporal aggregate network is another temporal multidimensional network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$ where $B=\{A'_i|A'_i \neq \ast\}$ and
	\begin{enumerate}
		\item $\Vr' \subseteq \Vr$ and $\forall [v]$, an equivalence class in $\Vr$, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$, $\exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$. The weight of $v'$, $W_{\Gr'}(v')$, is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
		\item \revision{Let $ [v] $ be an equivalence class of $ v $, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$. For each $ v\in \Vr $, $ \exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$}
%		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.
		\item $\forall u',v' \in \Vr'$ where $u' \leq v'$ and any $\Sr[i], i \in [1,t_{end}]$, if there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in \Sr[i],(u \in [u'] \wedge v \in [v']) \vee (u \in [v'] \wedge v \in [u']) \}$, then $ \exists (u',v',a') \in \Sr'[i] $, where $a'$ is the aggregation result of numeric attributes of edges in $E$ obtained by aggregation function upon edges specified by user.
	\end{enumerate}
\end{definition}
In short, conducting aggregations on temp-multi-network contains two stages: aggregating, or group-by on the vertex table as 1) in Definition~\ref{def:temp_aggregate_network} and aggregating each snapshots in the temp-multi-network as 2) in Definition~\ref{def:temp_aggregate_network}.

>>>>

\begin{definition}[Temporal Aggregate Network]
	\label{def:temp_aggregate_network}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$ and an aggregation $A'=(A'_1,A'_2,...,A'_n)$ where $A'_i$ equals $A_i$ or $\ast$, the obtained temporal aggregate network is another temporal multidimensional network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$ where $\Vr' \subseteq \Vr$, $B=\{A'_i|A'_i \neq \ast\}$ and
	\begin{enumerate}
		\item \revision{Let $ [v] $ be an equivalence class of $ v $, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$. For each $ v\in \Vr $, $ \exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$.} $W_{\Gr'}(v')$ is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
%		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.
		\item $\forall u',v' \in \Vr'$ where $u' \leq v'$ and any $\Sr[i], i \in [1,t_{end}]$, if there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in \Sr[i],(u \in [u'] \wedge v \in [v']) \vee (u \in [v'] \wedge v \in [u']) \}$, then $ \exists (u',v',a') \in \Sr'[i] $, where $a'$ is the aggregation result of numeric attributes of edges in $E$ obtained by aggregation function upon edges specified by user.
	\end{enumerate}
\end{definition}
In short, conducting aggregations on temp-multi-network contains two stages: aggregating, or group-by on the vertex table as 1) in Definition~\ref{def:temp_aggregate_network} and aggregating each snapshots in the temp-multi-network as 2) in Definition~\ref{def:temp_aggregate_network}.
